GPU-friendly Stroke Expansion

### 2024-06-14 paper.tex
Fixes to code formatting and wording

\begin{algorithm}
  $tid \gets$ global invocation ID\;
  $(style, segment) \gets readScene(tid)$\;
  \eIf{$style$ is $fill$}{
      \tcp{Output source curve}
      flatten\_cubic(segment, $0$)\;
  }{
      \tcp{Handle stroked segment}
      \eIf{$segment$ is \emph{stroke cap marker}}{
          \eIf{path is open}{output start cap\;}{output nothing\;}
      }{
          \tcp{Output both offset curves}
          flatten\_cubic(segment,  style.offset)\;
          flatten\_cubic(segment, -style.offset)\;

@@

\begin{algorithm}
\SetKwProg{Fn}{fn}{}{end}
\SetKwBlock{Loop}{loop}{end}
\Fn{flatten\_cubic(cubic: Cubic, offset: f32)}{
    TOL $\gets$ Euler spiral fit tolerance\;
    \tcp{`t0\_u' and `dt' track the recursion stack}
    t0\_u $\gets$ 0u\;
    dt $\gets$ 1.0\;
    last\_p $\gets$ cubic.p0\;
    last\_q $\gets$ cubic.p1 - cubic.p0\;
    \Loop{
        t0 $\gets$ f32(t0\_u) * dt\;
        \If{dt == 1.0}{break\;}
        t1 $\gets$ t0 + dt\;
        (next\_p, next\_q) $\gets$ eval\_cubic\_and\_deriv(cubic, t1)\;
        \tcp{Estimate error of geometric}
        \tcp{Hermite interpolation to Euler spiral}
        \nosemic(th0, th1, chord\_len, err) $\gets$ fit\_cubic\_to\_es(\;
        \pushline\dosemic last\_p, next\_p, last\_q, next\_q, dt)\;
        \popline \eIf{err <= TOL}{
            es $\gets$ euler\_segment(th0, th1, last\_p, next\_p)\;
            \tcp{Find location of any cusp in outline.}
            \tcp{If $0 \leq t < 1$, draw evolute at `t'.}
            cusp0 $\gets$ es\_curvature(es, 0) * offset + chord\_len\;
            cusp1 $\gets$ es\_curvature(es, 1) * offset + chord\_len\;
            t $\gets$ cusp0 * cusp1 >= 0 ? 1 : cusp0 / (cusp0 - cusp1)\;
            \If{cusp0 >= 0}{
                evolute\_finalize()\;
                es\_seg\_flatten\_offset(es, offset, vec2(0, t))\;
            }
            \If{cusp0 < 0 OR t < 1}{
                evolute\_start(es, offset)\;
                range $\gets$ cusp0 >= 0 ? vec2(t, 1) : vec2(0, t)\;
                es\_seg\_flatten\_evolute(es, range)\;
                es\_seg\_flatten\_offset\_reverse(es, offset, range)\;
            }
            \If{cusp0 < 0 AND t < 1}{
                evolute\_finalize()\;
                es\_seg\_flatten\_offset(es, offset, vec2(t, 1))\;
            }
            \tcp{Pop the stack}
            t0\_u $\gets$ t0\_u + 1u\;
            shift $\gets$ countTrailingZeros(t0\_u)\;
            t0\_u $\gets$ t0\_u >> shift;
            dt $\gets$ dt * f32(1u << shift)\;
            last\_p $\gets$ next\_p\;
            last\_q $\gets$ next\_q\;
        }{
            \tcp{Error is above the tolerance.}
            \tcp{Push the stack; Continue subdivision}
            t0\_u $\gets$ t0\_u * 2u\;
            dt $\gets$ dt * 0.5\;
        }
    }
}
\caption{Outline of the iterative cubic Bézier flattening routine invoked in our compute shader. A working WGSL implementation is provided in the supplemental materials.}
\label{alg:flatten-cubic}
\end{algorithm}

>>>>

\begin{algorithm}
  $tid \gets$ global invocation ID\;
  $(style, segment) \gets readScene(tid)$\;
  \eIf{$style$ is $fill$}{
      \tcp{Output source curve (offset = 0)}
      flatten\_cubic(segment, $0$)\;
  }{
      \tcp{Handle stroked segment}
      \eIf{$segment$ is \emph{stroke cap marker}}{
          \eIf{path is open}{output start cap\;}{output nothing\;}
      }{
          \tcp{Output parallel curves}
          flatten\_cubic(segment,  style.offset)\;
          flatten\_cubic(segment, -style.offset)\;

@@

\begin{algorithm}
\SetKwProg{Fn}{fn}{}{end}
\SetKwBlock{Loop}{loop}{end}
\Fn{flatten\_cubic(cubic: Cubic, offset: f32)}{
    TOL $\gets$ Euler spiral fit tolerance\;
    \tcp{`t0\_u' and `dt' track the recursion stack}
    t0\_u $\gets$ 0u\;
    dt $\gets$ 1.0\;
    last\_p $\gets$ cubic.p0\;
    last\_q $\gets$ cubic.p1 - cubic.p0\;
    \Loop{
        t0 $\gets$ f32(t0\_u) * dt\;
        \If{dt == 1.0}{break\;}
        t1 $\gets$ t0 + dt\;
        (next\_p, next\_q) $\gets$ eval\_cubic\_and\_deriv(cubic, t1)\;
        \tcp{Estimate error of geometric}
        \tcp{Hermite interpolation to Euler spiral}
        \nosemic(th0, th1, chord\_len, err) $\gets$ fit\_cubic\_to\_es(\;
        \pushline\dosemic last\_p, next\_p, last\_q, next\_q, dt)\;
        \popline \eIf{err <= TOL}{
            es $\gets$ euler\_segment(th0, th1, last\_p, next\_p)\;
            \tcp{Find location of any cusp in outline.}
            \tcp{If $0 \leq t < 1$, draw evolute at `t'.}
            cusp0 $\gets$ es\_curvature(es, 0) * offset + chord\_len\;
            cusp1 $\gets$ es\_curvature(es, 1) * offset + chord\_len\;
            t $\gets$ cusp0 * cusp1 >= 0 ? 1 : cusp0 / (cusp0 - cusp1)\;
            \If{cusp0 >= 0}{
                evolute\_finalize()\;
                es\_seg\_flatten\_offset(es, offset, vec2(0, t))\;
            }
            \If{cusp0 < 0 OR t < 1}{
                evolute\_start(es, offset)\;
                range $\gets$ cusp0 >= 0 ? vec2(t, 1) : vec2(0, t)\;
                es\_seg\_flatten\_evolute(es, range)\;
                es\_seg\_flatten\_offset\_reverse(es, offset, range)\;
            }
            \If{cusp0 < 0 AND t < 1}{
                evolute\_finalize()\;
                es\_seg\_flatten\_offset(es, offset, vec2(t, 1))\;
            }
            \tcp{Pop the stack}
            t0\_u $\gets$ t0\_u + 1\;
            shift $\gets$ countTrailingZeros(t0\_u)\;
            t0\_u $\gets$ t0\_u $\gg$ shift\;
            dt $\gets$ dt * f32(1 $\ll$ shift)\;
            last\_p $\gets$ next\_p\;
            last\_q $\gets$ next\_q\;
        }{
            \tcp{Error is above the tolerance.}
            \tcp{Push the stack; Continue subdivision}
            t0\_u $\gets$ t0\_u * 2\;
            dt $\gets$ dt * 0.5\;
        }
    }
}
\caption{Outline of the iterative cubic Bézier flattening routine invoked in our compute shader. A working WGSL implementation is provided in the supplemental materials.}
\label{alg:flatten-cubic}
\end{algorithm}
